Notes on scheduling the SAA2019 meeting

### 2017-11-03 analysis/paper/saa2018_nonposter_sessions_while_loop.Rmd
all papers allocated, no conflicts, plotted

```{r, setup, echo = FALSE, warning = FALSE, message = FALSE,}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "figures"
)

library(saaabstracts)
library(readxl)
library(tidyverse)
library(knitr)
library(kableExtra)
library(glue)
```
## Introduction

@@

@@

# how many unique general sessions? 
n_gen_sessions <- length(unique(gen_sessions$SESSION))

@@

# combine organised and general sessions
org_sessions$`Session Id` <- as.character(org_sessions$`Session Id`)
gen_sessions$`Session Id` <- gen_sessions$SESSION
gen_sessions$`Session Type` <- "Symposium"

@@

We have this many sessions in each major category:

@@

```{r}
saa_info_on_session_duration <- 
  read_excel("../data/raw_data/saa all organizedsession_timeslotABxls.xls", sheet = 2)

# omit rows with no session id
saa_info_on_session_duration <- 
  saa_info_on_session_duration %>% 
  filter(!is.na(`SESSION ID`)) %>% 
  mutate(`Session Id` = as.character(`SESSION ID`))

# join with our sessions 
all_nonposter_sessions_with_saa_info <- 
  all_nonposter_sessions %>% 
  left_join(saa_info_on_session_duration)

# papers in a session with saa info on duration 
all_nonposter_sessions_have_saa_info <- 
  all_nonposter_sessions_with_saa_info %>% 
    filter(!is.na(TYPE))

# papers in a session without saa infor on duration (general sessions?)
all_nonposter_sessions_not_have_saa_info <- 
  all_nonposter_sessions_with_saa_info %>% 
  filter(is.na(TYPE))
```

@@

# get the number of the start slot to go with the number of the end slot
 xx$start <- 0
for(i in 1:(nrow(xx))) {
  xx$start[i] <- 
    if_else(i == 1, 
           1,
            as.numeric(xx[ i-1, 2]) + 1)
}
# each slot is 4 hours long
total_cap <- 
  xx %>% 
  mutate(total_capacity = slot * 4) %>% 
  select(day_part, slot, total_capacity)
total_cap
```

Now we will takesession from the big table of sessions and add it into, for example, Th-morning. We'll keep adding more sessions until we reach the capacity of that day-part.

@@

```{r while-loop, echo = TRUE, eval = TRUE}

# get all the sessions, but we're going to modify this, so make a copy
all_nonposter_sessions_have_saa_info$session_time_allowed <- 
  as.numeric(all_nonposter_sessions_have_saa_info$TIME)
z7 <- all_nonposter_sessions_have_saa_info
all_of_the_day_parts <- NULL
total_cap$hours_of_sessions <- 0
total_cap$n_sessions <- 0
total_cap$c_sessions <- 0
container_for_this_day_part_with_day_from_while <- 0
i <- 1

@@

  target_capacity <- total_cap$total_capacity[i] - 4

  # prepare a while statement that will take a session, 
  # check to see if there is a name clash with sessions,
  # skip adding it if there is clash, then check to see
  # the culumative duration of the sessions in the day-part 
  # has exceeeded the total duration of the day-part,
  # and stop adding sessions if it has.

@@

    # get the names of all the people in this session...
    all_the_people_in_this_session <- 
      all_nonposter_sessions_have_saa_info %>% 
      filter(`Session Id` == get_a_session$`Session Id`)

@@

# out put the results
write.csv(all_of_the_day_parts, 
          "../data/derived_data/output_of_day_part_classification.csv")
```

@@

```{r while-loop-testing, results = 'hide'}
# check to see what we got from the loop...
sessions_per_day <- 
all_of_the_day_parts %>% 
  group_by(day_part_from_while) %>% 
  summarise(n_sessions = length(unique(`Session Id`)))

@@

n_missing_papers <- 
  nrow(all_nonposter_sessions) - nrow(all_of_the_day_parts)

n_missing_sessions <- 
  length(unique(all_nonposter_sessions$`Session Id`)) - length(unique(all_of_the_day_parts$`Session Id`))

missing_sessions <- 
  unique(all_nonposter_sessions$`Session Id`)[!(unique(all_nonposter_sessions$`Session Id`) %in% unique(all_of_the_day_parts$`Session Id`)) ]

@@

@@

Now we've got all the organised sessions scheduled into day-parts with no clashes.

@@

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository("../..")
```

>>>>

```{r, setup, echo = FALSE, warning = FALSE, message = FALSE,}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "figures"
)

library(saaabstracts)
library(readxl)
library(tidyverse)
library(knitr)
library(glue)

```
## Introduction

@@

gen_sessions <- 
gen_sessions %>% 
  mutate(`Session Id` = SESSION) %>% 
  mutate(`Session Id` =  ifelse(`Session Id` == "35B",
          max(as.numeric(`Session Id`), na.rm = TRUE) + 1, 
          as.numeric(`Session Id`) ))

@@

# how many unique general sessions? 
n_gen_sessions <- length(unique(gen_sessions$`Session Id`))

@@

# combine organised and general sessions
org_sessions$`Session Id` <- as.numeric(org_sessions$`Session Id`)
gen_sessions$`Session Type` <- "Symposium"

@@

We have this many sessions in each major category, according to my tally of the individual papers:

@@

```{r}
saa_info_on_organised_session_duration <- 
  read_excel("../data/raw_data/saa all organizedsession_timeslotABv3.xls", sheet = 2) %>% 
  mutate(`Session Id` = `SESSION ID`)

computed_general_session_duration <- 
  gen_sessions %>% 
  group_by(`Session Id`) %>% 
  summarise(n_papers = n()) %>% 
  mutate(TIME = n_papers * 0.25) %>%  # 15 mins per paper
  mutate(`Session Id` =  ifelse(`Session Id` == "35B",
          max(as.numeric(`Session Id`), na.rm = TRUE) + 1, 
          as.numeric(`Session Id`) ))

# combine general and organised session durations
org_and_gen_session_durations <- 
  saa_info_on_organised_session_duration %>% 
  filter(!is.na(`Session Id`)) %>% 
  mutate(n_papers = `N papers`,
         TIME = as.numeric(TIME)) %>% 
  select(`Session Id`, TIME, n_papers) %>% 
  rbind(computed_general_session_duration) %>% 
  filter(!is.na(TIME)) %>% 
  # add 15 m min  to each session for a changeover time
  mutate(TIME = if_else(TIME == 4.0, 
                        TIME,
                        TIME + 0.25))

head(org_and_gen_session_durations)

# join the session duration onto each paper

all_nonposter_sessions_with_session_durations <- 
  all_nonposter_sessions %>% 
  mutate(`Session Id` = as.numeric(`Session Id`)) %>% 
  left_join(org_and_gen_session_durations)

head(all_nonposter_sessions_with_session_durations)
```

@@

# get the number of the start slot to go with the number of the end slot
 xx$start <- 0
for(i in 1:(nrow(xx))) {
  xx$start[i] <- 
    if_else(i == 1, 
           1,
            as.numeric(xx[ i-1, 2]) + 1)
}
# each slot is 4 hours long
total_cap <- 
  xx %>% 
  mutate(total_capacity = slot * 4) %>% 
  select(day_part, slot, total_capacity)

# View
total_cap
```

Now we will take session from the big table of sessions and add it into, for example, Th-morning. We'll keep adding more sessions until we reach the capacity of that day-part.

@@

```{r while-loop, echo = TRUE, eval = TRUE cache = TRUE}

# prepare some variables... get all the sessions, 
# but we're going to modify this, so make a copy
org_and_gen_session_durations$session_time_allowed <- 
  as.numeric(org_and_gen_session_durations$TIME)
all_nonposter_sessions_with_session_durations$session_time_allowed <- 
  all_nonposter_sessions_with_session_durations$TIME
z7 <- all_nonposter_sessions_with_session_durations
all_of_the_day_parts <- NULL
total_cap$hours_of_sessions <- 0
total_cap$n_sessions <- 0
total_cap$c_sessions <- 0
container_for_this_day_part_with_day_from_while <- 0
i <- 1

@@

  # add some buffer time to nudge it back so we don't overfill a day-part
  # maybe if this buffer is bigger, the knapsack will be faster?
  # A big enough buffer should avoid the 0 group in the knapsack results
  # which indicates that the knapsack fn can't fit all the sessions in the
  # day-part
  buffer <- 30
  target_capacity <- total_cap$total_capacity[i] - buffer

  # prepare a while statement that will take a session, 
  # check to see if there is a name clash with sessions,
  # skip adding it if there is clash, then check to see
  # the cumulative duration of the sessions in the day-part 
  # has exceeded the total duration of the day-part,
  # and stop adding sessions if it has.

@@

    # get the names of all the people in this session...
    all_the_people_in_this_session <- 
      all_nonposter_sessions_with_session_durations %>% 
      filter(`Session Id` == get_a_session$`Session Id`)

@@

# out put the results
write.csv(all_of_the_day_parts, 
          "../data/derived_data/output_of_day_part_classification.csv")

write.csv(total_cap, "../data/derived_data/total_cap.csv")
```

```{r}
# read them in, if we need to
all_of_the_day_parts <- readr::read_csv("../data/derived_data/output_of_day_part_classification.csv")

total_cap <- readr::read_csv("../data/derived_data/total_cap.csv")
```

@@

```{r while-loop-testing, results = 'hide', echo = TRUE}
# check to see what we got from the loop...
sessions_per_day <- 
all_of_the_day_parts %>% 
  group_by(day_part_from_while) %>% 
  summarise(n_sessions = length(unique(`Session Id`)))

@@

n_missing_papers <- 
  nrow(all_nonposter_sessions_with_session_durations) - nrow(all_of_the_day_parts)

n_missing_sessions <- 
  length(unique(all_nonposter_sessions_with_session_durations$`Session Id`)) - length(unique(all_of_the_day_parts$`Session Id`))

missing_sessions <- 
  unique(all_nonposter_sessions_with_session_durations$`Session Id`)[!(unique(all_nonposter_sessions_with_session_durations$`Session Id`) %in% unique(all_of_the_day_parts$`Session Id`)) ]

@@

## Organise the sessions in each day-part into 4 hour slots

Now that we have allocated all the organised sessions into day-parts, we need to group them into 4 hour slots so we can assign them to specific rooms.

We can use the mulitple knapsack algorithm for this. For example, Thurs morning has 36 slots of 4 hours each.

We have a series of functions, one for each day-part, then we run them, and write the output to CSV.

```{r}
# thu-morning

thu_mo <- function(){

# get the slots available for this day-part
thu_morning_slots <- 
  total_cap %>% 
  filter(day_part == 'Th-morning') %>% 
  pull(slot)

# get the session id's assigned to this day-part
thu_morning_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Th-morning') %>% 
  slice(1)

slots_to_fill <- rep(4, thu_morning_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- thu_morning_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

thu_morning_sessions$computed_slot <- solution$ksack

write.csv(thu_morning_sessions,
          "../data/derived_data/thu_morning_sessions.csv")
}

# Here's thursday afternoon:

# thu-afternoon
thu_af <- function(){

# get the slots available for this day-part
thu_afternoon_slots <- 
  total_cap %>% 
  filter(day_part == 'Th-afternoon') %>% 
  pull(slot)

# get the session id's assigned to this day-part
thu_afternoon_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Th-afternoon') %>% 
  slice(1)

slots_to_fill <- rep(4, thu_afternoon_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- thu_afternoon_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

thu_afternoon_sessions$computed_slot <- solution$ksack

write.csv(thu_afternoon_sessions, 
          "../data/derived_data/thu_afternoon_sessions.csv")
}

# Here's thursday evening:

# thu-evening

thu_ev <- function(){

# get the slots available for this day-part
thu_evening_slots <- 
  total_cap %>% 
  filter(day_part == 'Th-evening') %>% 
  pull(slot)

# get the session id's assigned to this day-part
thu_evening_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Th-evening') %>% 
  slice(1)

slots_to_fill <- rep(4, thu_evening_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- thu_evening_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

thu_evening_sessions$computed_slot <- solution$ksack

write.csv(thu_evening_sessions, 
          "../data/derived_data/thu_evening_sessions.csv")
}

# Here's friday morning:

# fri-morning

fri_mo <- function(){

# get the slots available for this day-part
fri_morning_slots <- 
  total_cap %>% 
  filter(day_part == 'Fr-morning') %>% 
  pull(slot)

# get the session id's assigned to this day-part
fri_morning_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Fr-morning') %>% 
  slice(1)

slots_to_fill <- rep(4, fri_morning_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- fri_morning_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

fri_morning_sessions$computed_slot <- solution$ksack

write.csv(fri_morning_sessions, 
          "../data/derived_data/fri_morning_sessions.csv")
}

# Here's friday afternoon:

# fri-afternoon

fri_af <- function(){

# get the slots available for this day-part
fri_afternoon_slots <- 
  total_cap %>% 
  filter(day_part == 'Fr-afternoon') %>% 
  pull(slot)

# get the session id's assigned to this day-part
fri_afternoon_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Fr-afternoon') %>% 
  slice(1)

slots_to_fill <- rep(4, fri_afternoon_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- fri_afternoon_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

fri_afternoon_sessions$computed_slot <- solution$ksack

write.csv(fri_afternoon_sessions, 
          "../data/derived_data/fri_afternoon_sessions.csv")
}

# Here's Saturday morning:

# sat-morning
sat_mo <- function(){

# get the slots available for this day-part
sat_morning_slots <- 
  total_cap %>% 
  filter(day_part == 'Sa-morning') %>% 
  pull(slot)

# get the session id's assigned to this day-part
sat_morning_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Sa-morning') %>% 
  slice(1)

slots_to_fill <- rep(4, sat_morning_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- sat_morning_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

sat_morning_sessions$computed_slot <- solution$ksack

write.csv(sat_morning_sessions, 
          "../data/derived_data/sat_morning_sessions.csv")
}

# Here's saturday afternoon:

# sat-afternoon

sat_af <- function(){

# get the slots available for this day-part
sat_afternoon_slots <- 
  total_cap %>% 
  filter(day_part == 'Sa-afternoon') %>% 
  pull(slot)

# get the session id's assigned to this day-part
sat_afternoon_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Sa-afternoon') %>% 
  slice(1)

slots_to_fill <- rep(4, sat_afternoon_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- sat_afternoon_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

sat_afternoon_sessions$computed_slot <- solution$ksack

write.csv(sat_afternoon_sessions, 
          "../data/derived_data/sat_afternoon_sessions.csv")
}

# Here's sunday morning:

# sun-morning
sun_mo <- function(){

# get the slots available for this day-part
sun_morning_slots <- 
  total_cap %>% 
  filter(day_part == 'Su-morning') %>% 
  pull(slot)

# get the session id's assigned to this day-part
sun_morning_sessions <- 
  all_of_the_day_parts %>% 
  group_by(`Session Id`) %>% 
  filter(day_part_from_while == 'Su-morning') %>% 
  slice(1)

slots_to_fill <- rep(4, sun_morning_slots) * 60 # so many 4 hour slots that we need to fill

sessions_we_have <- sun_morning_sessions$session_time_allowed * 60

library(adagio)
# mknapsack calling signature is: mknapsack(values, weights, capacities)
solution <- mknapsack(sessions_we_have, 
                      sessions_we_have,
					  slots_to_fill)

sun_morning_sessions$computed_slot <- solution$ksack

write.csv(sun_morning_sessions, 
          "../data/derived_data/sun_morning_sessions.csv")
}

```{r}
# run all of these
thu_mo()
thu_af()
thu_ev()
fri_mo()
fri_af()
sat_mo()
sat_af()
sun_mo()

# why do these sometime have a 0 group? Because the fn can't fit it all in! So we need to add more buffer to each day-part in the while loop
```

## Resolving conflicts with requested times

Now let's get all the names of the people in each day-part to check for the special requests that a few people have made:

```{r}

# read in the day-part data from the while-loop
sessions_in_day_parts <- list.files("../data/derived_data", pattern = "_sessions.csv", full.names = TRUE)
sessions_in_day_parts_data <- 
  map(sessions_in_day_parts, 
       ~read_csv(.x))

# for each day-part, join with the all names of the people in each session
sessions_in_day_parts_data_with_all_names <- 
  map(sessions_in_day_parts_data,
      ~.x %>% 
        left_join(all_of_the_day_parts, by = 'Session Id')
      )

# get day-parts to use in file names
day_parts_of_list <- 
  map_chr(sessions_in_day_parts_data_with_all_names, 
    ~unique(.x$day_part_from_while.y))

# write these out to CSV
walk2(sessions_in_day_parts_data_with_all_names, 
     day_parts_of_list,
     ~write_csv(.x,  path = glue("../data/derived_data/{.y}-all-names.csv")))

# any computer slots with 0?
sessions_in_day_parts_data_with_all_names_df <- 
bind_rows(sessions_in_day_parts_data_with_all_names)

sessions_in_day_parts_data_with_all_names_df %>% 
  filter(computed_slot == 0)
```

Sat morning is a focus of many of the special requests, let's have a look at that

```{r}
Sa_morning_names <- sessions_in_day_parts_data_with_all_names[[which(day_parts_of_list == "Sa-morning")]]

# read in the sheet on conflicts
conflicts <- read_excel("../data/raw_data/Conflicts.xlsx")
# make a unique name variable
conflicts$uid <- glue('{conflicts$PRENOM}_{conflicts$NOM}')
# get the ones for Sa-morning
Sa_morning_conflicts <- 
  conflicts %>% 
  filter(grepl("Sa", CONFLICTS))

# check to see if we have a problem
Sa_morning_conflict_result <- Sa_morning_names$uid.y[Sa_morning_names$uid.y %in% Sa_morning_conflicts$uid]

# double-check
double_check <- 
Sa_morning_names[Sa_morning_names$`Last Name.y` %in% Sa_morning_conflicts$NOM, ]
# it's ok
```

We have `r length(Sa_morning_conflict_result)` conflicts on Saturday morning, that's `r ifelse(length(Sa_morning_conflict_result) == 0, "great", "not ideal")`

What about conflicts in other day-parts?

```{r}
other_conflicts <- 
  conflicts %>% 
  filter(!grepl("Sa", CONFLICTS))
```

There are just `r nrow(other_conflicts)`, so let's do it one by one.

1. Deborah Nichols doesn't want to be in Thurs AM, Fri AM. When do we have her?

```{r}
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(uid.y == "Deborah_Nichols") %>% 
  select(`Session Id`, uid.y, day_part_from_while.y )
```

She's ok, great!

2. Leah McCurdy and session 3109, but what is the conflict exactly? Not on Sat morning from 9-11 am.

```{r}
Sa_morning_names %>% 
  filter(uid.y == "Leah_McCurdy")

# when is she?
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(uid.y == "Leah_McCurdy") %>% 
  select(day_part_from_while.y)
```

She's ok, oon Fr-morning

3. Session 2929 should not be on "Thurs PM, Thurs EVE, Fri PM, SAT AM, SAT PM". When do we have it?

```{r}
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(`Session Id` == 2929) %>% 
  select(`Session Id`, uid.y, day_part_from_while.y )
```

This is a problem, we put this session in Th-afternoon.

Can we tack it onto Su-morning, right at the end? According to the results of our while-loop, we have many hours spare on Su-morning:

```{r}
total_cap
```

Let's double-check what we've got after the multiple knapsack work:

```{r}
day_parts_filled_hours <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  group_by(`Session Id`) %>% 
  slice(1) %>% 
  group_by(day_part_from_while.y) %>% 
  summarise(hours_in_day_part = sum(session_time_allowed.y ))
```

It's the same. So how many spare hours do we have on Su-morning?

```{r}
Su_morning_hours_available <- 
total_cap %>% 
  filter(day_part == "Su-morning") %>% 
  select(total_capacity) %>% 
  pull()

Su_morning_hours_filled <- 
  day_parts_filled_hours %>% 
  filter(day_part_from_while.y == "Su-morning") %>% 
  select(hours_in_day_part) %>% 
  pull()

Su_morning_spare_hours <- 
  Su_morning_hours_available - Su_morning_hours_filled

We have `r Su_morning_spare_hours` hours unused on Sunday morning. Heaps of space. So let's move Session 2929 to Sunday morning:

```{r}
sessions_in_day_parts_data_with_all_names_df <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  mutate(day_part_from_while.y = if_else(`Session Id` == 2929, 
                                         "Su-morning", 
                                         day_part_from_while.y))

# check it
check_session_2929_to_sunday_morning <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  filter(`Session Id` == 2929) %>% 
  select(day_part_from_while.y) %>% 
  unique()

@@

Now we've got all the organised sessions scheduled into slots and day-parts with no clashes, and no conflicts with requested times.

```{r}
# this is our final result
write_csv(sessions_in_day_parts_data_with_all_names_df,
          "../data/derived_data/sessions_in_day_parts_data_with_all_names_df.csv")

# can we make a visual schedule?
x <- 
sessions_in_day_parts_data_with_all_names_df %>% 
  group_by(day_part_from_while.y, computed_slot) %>% 
  summarise(sessions_for_plot = toString(unique(`Session Id`)))

# put day-slots in order
x$day_part_from_while.y <- factor(x$day_part_from_while.y, 
                                  levels = total_cap$day_part)

ggplot(x,
       aes(day_part_from_while.y,
           computed_slot)) +
 geom_tile(colour = "black",
           fill = "white") +
  geom_text(aes(label = sessions_for_plot), 
                  size = 3) +
    scale_y_continuous(breaks = 0:max(x$computed_slot)) +
  theme_bw() +
  xlab("") +
  ylab("Room-ish") +
  ggtitle("Visual schedule for SAA2019 conference non-poster sessions",
          subtitle = "The numbers on the plot are the Session Ids. \n We can think of  each row as equivalent to a room at the conference venue. ")

ggsave("../figures/visual_schedule_for_saa2019_conference_non_poster_sessions.png")

@@

```{r}
# what commit is this file at? 
git2r::repository("../..")
```
